
\section*{Misc} 
  \resumeSubHeadingListStart
\resumeSubheading
{\href{https://github.com/meltq/QUANTUMOS}{Visualizing the temperature of a black hole}}
{}
    {}
    {}
    \resumeItemListStart
    \resumeItem {Won in the quantum track of Quantathon 1.0 with this project.}
    \resumeItem {Uses the mass of a black hole to plot its temperature varying by time using quantum computing.}
    \resumeItem {Could theoretically be used for detecting black holes.} \hfill \break
    \resumeItemListEnd

     \resumeSubheading
     {\href{https://github.com/meltq/app-mini-project}{Image classification using neural networks and edge
detection}}
{}
    {}
    {}
    \resumeItemListStart
    \resumeItem {Identifies different road signs using neural networks and edge detection.}
    \resumeItem {Uses edge detection to dramatically reduce the size of each image in the training data, therefore allowing for a larger number of images to train on.}
    \resumeItem {Considerably speeds up the classification process for most use cases while retaining the same accuracy.} \hfill \break 
    \resumeItemListEnd
  
  \resumeSubheading
  {\href{https://github.com/meltq/Framebuffer-rendering}{Framebuffer Rendering}}
{}
    {}
    {}
    \resumeItemListStart
    \resumeItem {Uses the framebuffer device on Linux systems to directly manipulate pixel memory data for on-screen display without any dependencies.}
    \resumeItem {Renders various visual formats including images, animated GIFs, and custom pixel data.}
    \resumeItem {Functions effectively within a Linux virtual terminal environment without a running display server.} \hfill \break
    \resumeItemListEnd

    \resumeSubheading
    {\href{https://courses.edx.org/certificates/7eda8fc61a0f44a19eb74222287097bf}{Compiler Design}}
{}
    {}
    {}
    \resumeItemListStart
    \resumeItem {Certification offered by StanfordOnline, an
online learning initiative of Stanford University.}
    \resumeItem {Learned how to build different stages of a compiler using formal languages and different pitfalls of the different methods used at each stage.} \hfill \break 
    \resumeItemListEnd

  \resumeSubHeadingListEnd


