% Project 1
\resumeSubheading
{Linux Kernel}{Jun.\@ 2024 \textbf{-} Present}
{\href{https://gitlab.freedesktop.org/drm/misc/kernel/-/commits/drm-misc-next?search=Tejas+Vipin}{Contributor to DRM subsystem}}
{}
\resumeItemListStart
\resumeItem {The Direct Rendering Manager is a subsystem in the kernel that contains the code and drivers for managing graphics related hardware.}
\resumeItem {Optimized several display panels that use MIPI DSI by reducing generated code size and improving the internal API.}
% \resumeItem {Modified the MIPI DSI api to use functions that can do error handling and error checking better.} \hfill \break
\resumeItemListEnd
% Project 2
\resumeSubheading
{LLVM}{Jan.\@ 2025 \textbf{-} Present}
{\href{https://github.com/llvm/llvm-project/issues?q=is\%3Apr\%20author\%3Ameltq\%20}{Contributor to MLIR, Libc}}
{}
\resumeItemListStart
\resumeItem {LLVM is a modular, open-source compiler framework designed to optimize and generate intermediate and machine-level code for a wide range of programming languages and architectures.}
\resumeItem {Optimized MLIR generation for operations involving 0 dimensional vectors. Optimized and worked on unit test architecture involving the same.}
\resumeItem {Implemented higher order math functions like asinh and hypot for Float16 in libc and wrote exhaustive tests for them.}
\resumeItem {Profiled different function implementations and identified performance bottlenecks and removed them.}
\resumeItemListEnd

% \resumeSubheading
% {Wayland}{Jul.\@ 2024 \textbf{-} Present}
% {\href{https://gitlab.freedesktop.org/wayland/wayland/-/commits/main?search=meltq}{Contributor to Wayland core protocol}}
% {}
% \resumeItemListStart
% \resumeItem {Wayland is a modern display server protocol for Linux and other Unix-like operating systems.}
% \resumeItem {Streamlined error handling in several parts of the core wayland protocol.}
% \resumeItemListEnd

\resumeSubHeadingListEnd
\pagebreak